Autonomous Oceanographic Sampling Designs using Excursion Sets for Multivariate Gaussian random fields

### 2020-06-04 main_new.tex
updates

\begin{figure}[!h] 
  \centering 
  \subfigure[Illustration of an ocean sensing network and the sense-plan-act control methodology.]{\includegraphics[width =
    0.49\textwidth]{Figures/envir2.pdf}\label{fig:envir1}}
  \hfill
  \subfigure[Frontal patterns off of the Nidelva river, Trondheim, Norway.]{\includegraphics[width =
    0.49\textwidth]{Figures/river_proccess.pdf}\label{fig:nidelven}}
  \caption{\ref{fig:envir1} Traditional ocean observation based on 
    ship-based sampling has been augmented by autonomous
    robotic vehicles. % and their interactions.  
    AUV platforms are an integral part of this network being able to
    reason and make decisions for efficient onboard adaptive sampling.
    % using the sense-plan-act control approach to autonomous control. 
    \ref{fig:nidelven} The interaction of river and ocean creates
    processes that are challenging to map, where the combination of
    statistics and robotics can play a vital role in enabling more
    effective oceanographic observation.\kc{The inset ``AUV robot''
      looks very tacky and ad-hoc; might be best to remove it. Why not
      add a subfigure of an AUV instead and not lump it into a figure
      which is already quite busy? It can't hurt. Change ``ships'' to
      ``Ship'', remove the aerial drone, since we didn't use it and
      don't plan to in this work.}}
  \label{fig:envir} \end{figure}

@@

Assuming now that $q$ observations are available, one wishes to
predict $\gp[\bu]$, the multivariate Kriging equations holds with size
$p$ vector of conditional means \kc{This last sentence doesn't parse.
  Are they two separate statements?}:  
\begin{equation}\label{eq:cokrig}
\bbm(\x)=\bmu(\x)+\blambda(\x,\bu_d)^T \left( \by_d-\bG_d \bmu(\bu_d)\right),
\end{equation}
where $\bmu$ is size $p$ unconditional mean function of $Z$, $\by_d$ is the realized vector of observed responses, and $\blambda(\x,\bu_d)=\bK^{-1}_y(\bu_d,\bu_d) \bk(\bu_d, \bu)$. Here, the data covariance is $K_y=\mbox{Cov}(\bY_d,\bY_d)=\bG_d\bK(\bu_d,\bu_d)\bG_d^T+\bR_d$ and the cross-covariance is $\mbox{Cov}(\bY_d,Z(\x)) \bk(\bu_d, \x)=$, assuming the measurement error is independent of the GP.  The Kriging (cross-)covariance function can also be expressed in the same vein via $p \times p$ matrix
\begin{equation}\label{eq:krig:cov}
\bSigma(\x,\x')=\bK(\x,\x')-\blambda(\x,\bu_d)^T \bK_y(\bu_d, \bu_d) \lambda(\x,\bu_d).
\end{equation}

@@

A critical element in the derivation of a closed-form for the EIBV is that the
conditional mean in Eq. \eqref{eq:cokrig} is a linear (affine) function of
the data $\by_d$ and the covariance is not a function of the data. This in turn means that the probabilities in expression \eqref{eq:post_ep} involve inequality statements for linear combinations of Gaussian variables. 
Related closed-form solutions have been noted in similar contexts \citep{bhattacharjya2013value, chevalier2014fast,stroh}, but not generalized to our situation with random sets for vector-valued GPs.
Notably, the mean in equation \eqref{eq:cokrig}, is in the form of $\ba+\bB \bV$, where $\bV \sim N(0_q, \bK_y (\bu_d,\bu_d))$, $\ba=(t_1,t_2)^t-\bmu(\bu)-\blambda(\bu,\bu_d)^T \bG_d \bmu(\bu_d)$ and $\bB=\blambda(\bu,\bu_d)^T$.
The following then applies to give a closed-form solution to EIBV calculation in this case.

@@

In the more general case, for instance that of volumes of random sets, the criterion will include couplings  with different locations and the result must be generalized. For the case of multivariate monomials in orthant probabilities with thresholds affine in a common Gaussian vector. 
%Namely, for monomials of degree $k$, we have.

>>>>

\begin{figure}[!h] 
  \centering 
  \subfigure[Illustration of an ocean sensing network and the sense-plan-act control methodology.]{\includegraphics[width =
    0.49\textwidth]{Figures/envir2.pdf}\label{fig:envir1}}
  \hfill
  \subfigure[Frontal patterns off of the Nidelva river, Trondheim, Norway.]{\includegraphics[width =
    0.49\textwidth]{Figures/river_proccess.pdf}\label{fig:nidelven}}
  \caption{\ref{fig:envir1} Traditional ocean observation based on 
    ship-based sampling has been augmented by autonomous
    robotic vehicles. % and their interactions.  
    AUV platforms are an integral part of this network being able to
    reason and make decisions for efficient onboard adaptive sampling.
    % using the sense-plan-act control approach to autonomous control. 
    \ref{fig:nidelven} The interaction of river and ocean creates
    processes that are challenging to map, where the combination of
    statistics and robotics can play a vital role in enabling more
    effective oceanographic observation.\kc{The inset ``AUV robot''
      looks very tacky and ad-hoc; might be best to remove it. Change
      ``ships'' to
      ``Ship'', remove the aerial drone, since we didn't use it and
      don't plan to in this work.}}
  \label{fig:envir} \end{figure}

@@

Assuming now that $q$ observations are available, one wishes to
predict $\gp[\bu]$, the multivariate Kriging equations holds with size
$p$ vector of conditional means \kc{This last sentence doesn't parse.
  Are they two separate statements?}:  
\begin{equation}\label{eq:cokrig}
\bbm(\x)=\bmu(\x)+\blambda(\x,\bu_d)^T \left( \by_d-\bG_d \bmu(\bu_d)\right),
\end{equation}
where $\bmu$ is size $p$ unconditional mean function of $Z$, $\by_d$
is the realized vector of observed responses, and
$\blambda(\x,\bu_d)=\bK^{-1}_y(\bu_d,\bu_d) \bk(\bu_d, \bu)$. Here,
the data covariance is
$K_y=\mbox{Cov}(\bY_d,\bY_d)=\bG_d\bK(\bu_d,\bu_d)\bG_d^T+\bR_d$ and
the cross-covariance is $\mbox{Cov}(\bY_d,Z(\x)) \bk(\bu_d, \x)=$,
\kc{There is a dangling '='. Is this legit?} assuming the measurement
error is independent of the GP.  The Kriging 
(cross-)covariance function can also be expressed in the same vein via
a $p \times p$ matrix 
\begin{equation}\label{eq:krig:cov}
\bSigma(\x,\x')=\bK(\x,\x')-\blambda(\x,\bu_d)^T \bK_y(\bu_d, \bu_d) \lambda(\x,\bu_d).
\end{equation}

@@

A critical element in the derivation of a closed-form for the EIBV is
that the conditional mean in Eq. \eqref{eq:cokrig} is a linear
(affine) function of the data $\by_d$ and the covariance is not a
function of the data. This in turn means that the probabilities in
\eqref{eq:post_ep} involve inequality statements for linear
combinations of Gaussian variables. Related closed-form solutions have
been noted in similar contexts \citep{bhattacharjya2013value,
  chevalier2014fast,stroh}, but not generalized to our situation with
random sets for vector-valued GPs. Notably, the mean in equation
\eqref{eq:cokrig}, is in the form of $\ba+\bB \bV$, where
$\bV \sim N(0_q, \bK_y (\bu_d,\bu_d))$,
$\ba=(t_1,t_2)^t-\bmu(\bu)-\blambda(\bu,\bu_d)^T \bG_d \bmu(\bu_d)$
and $\bB=\blambda(\bu,\bu_d)^T$. The following then applies to give a
closed-form solution to EIBV calculation in this case.

@@

In the more general case, for instance that of volumes of random sets,
the criterion will include couplings with different locations and the
result must be generalized. For the case of multivariate monomials in
orthant probabilities with thresholds affine in a common Gaussian
vector \kc{This sentence is dangling. Doesn't have a conclusion.}.
%Namely, for monomials of degree $k$, we have.
